---
title: "Avaialable Sybiota Portals"
author: "Franz-Sebastian Krah"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Available Symbiota Portals}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Symbiota portals

## For general information
http://symbiota.org

## For an overview of Symbiota portals
http://symbiota.org/docs/symbiota-introduction/active-symbiota-projects/

## For an introductory tutorial 
https://github.com/FranzKrah/rSymbiota

## List of portals
```{r setup, include = TRUE, eval= FALSE}
library(rSymbiota)
portals()[,1]
```

## General usage

The function *symbiota* returns a S4 class object, which means that contents can be accesses using '@'. But there is also a generic function of the package that extracts the table from the class: *recordsTable*. Here an example:

```{r usage, include=TRUE, eval=FALSE}
spec.dist <- symbiota(taxon = "Amanita muscaria", db = "mycoportal", verbose = TRUE)

# This will give the actual records table downloaded from MyCoPortal.
recordsTable(spec.dist)
```


## Currently supported portals by rSymbiota

Please note that more portals are currently available than displayed on the Symbiota website (http://symbiota.org). The website will be updated soon to reflect that update. New portals will be continuously added here. If you have a new portal, please let us know so we can add it. Please futher note that there are redundancies between the portals, however, we listet all avaiable portals here for full transparency.

```{r supported, include = TRUE, eval= FALSE}

## you might need to increase wait, e.g. wait = 5 depending on the speed of your internet connection

## (1) MyCoPortal
spec.dist <- symbiota(taxon = "Amanita muscaria", db = "mycoportal", wait = 3)


## (2) Symbiota Collections of Arthropods Network
spec.dist <- symbiota(taxon = "Aedes aegypti", db = "SCAN", screenshot = TRUE)


## (3) Consortium of North American Bryophyte Herbaria
spec.dist <- symbiota(taxon = "Funaria hygrometrica", db = "bryophyte")


## (4) Frullania Collaborative Research Network
spec.dist <- symbiota(taxon = "Frullania", db = "frullania")


## (5) InvertEBase Data Portal
spec.dist <- symbiota(taxon = "Clitellata", db = "invertebase")


## (6) Consortium of North American Lichen Herbaria
## (7) Arctic Lichen Flora
spec.dist <- symbiota(taxon = "Parmelia", db = "lichen")


## (8) Smithsonian Tropical Research Institute Portal
spec.dist <- symbiota(taxon = "Atelopus", db = "STRI")


## (9) Aquatic Invasives
spec.dist <- symbiota(taxon = "Perciformes", db = "symbaquatic", taxon_type = 4)


## (10) Consortium of Midwest Herbaria
spec.dist <- symbiota(taxon = "Hamamelis", db = "Midwest Herbaria")


## (11) SEINet
spec.dist <- symbiota(taxon = "Sambucus", db = "SEINet")


## (12) Intermountain Region Herbaria Network (IRHN)
spec.dist <- symbiota(taxon = "Carex microptera", db = "IRHN")


## (13) SouthEast Regional Network of Expertise and Collections (SERNEC)
spec.dist <- symbiota(taxon = "Diospyros", db = "SERNEC")


## (14) North American Network of Small Herbaria
spec.dist <- symbiota(taxon = "Ambrosia", db = "Small Herbaria")


## (15) Northern Great Plains Herbaria
spec.dist <- symbiota(taxon = "Parietaria", db = "Great Plains")


## (16) Consortium of Northeastern Herbaria (CNH)
spec.dist <- symbiota(taxon = "Lonicera", db = "symbcnh")


## (17) Madrean Archipelago Biodiversity Assessment (MABA) - Flora
spec.dist <- symbiota(taxon = "Anisacanthus", db = "symbflora")


## (18) Madrean Archipelago Biodiversity Assessment (MABA) - Fauna
spec.dist <- symbiota(taxon = "Ambystoma", db = "symbfauna")


## (19) Herbario Virtual Austral Americano
spec.dist <- symbiota(taxon = "Calendula", db = "symbhvaa")


## (20) CoTRAM – Cooperative Taxonomic Resource for Amer. Myrtaceae
spec.dist <- symbiota(taxon = "Campomanesia", db = "symbcotram")


## (21) Lepidoptera of North America Network (LepNet)
## Please use SCAN database
# spec.dist <- symbiota(taxon = "Lepidopa californica", db = "LepNet")


## (22) Neotropical Entomology
spec.dist <- symbiota(taxon = "Physonota", db = "symbneotropentomology")


## (23) Neotropical Flora
spec.dist <- symbiota(taxon = "Bignoniaceae", db = "symbneotropplants")


## (24) Monarch (California Academy of Sciences)
spec.dist <- symbiota(taxon = "Carnivora", db = "Monarch", taxon_type = 4)


## (25) Virtual Flora of Wisconsin
spec.dist <- symbiota(taxon = "Fragaria", db = "Wisconsin")


## (26) Red de Herbarios del Noroeste de México
spec.dist <- symbiota(taxon = "Perityle", db = "Red de Herbarios")


## (27) University of Colorado Herbarium
spec.dist <- symbiota(taxon = "Cypripedium", db = "Colorado")


## (28) OpenZooMuseu
spec.dist <- symbiota(taxon = "", db = "symbzoo")


## (29) Mid-Atlantic Herbaria Consortium
spec.dist <- symbiota(taxon = "Viburnum", db = "midatlanticherbaria")


## (30) Channel Islands Biodiversity Information System
spec.dist <- symbiota(taxon = "Lupinus", db = "CAL-IBIS")


## (31) Consortium of Small Vertebrate Collections (CSVColl)
spec.dist <- symbiota(taxon = "Carnivora", db = "CSVColl", taxon_type = 4)


## (32) The Open Herbarium
spec.dist <- symbiota(taxon = "Biarum", db = "symbhereb")
## website did not load the last time I checked


## (33) Documenting Ethnobiology in Mexico and Central America
spec.dist <- symbiota(taxon = "Lamiaceae", db = "demca")


## (34) Consortium of Pacific Herbaria
spec.dist <- symbiota(taxon = "Asteraceae", db = "Pacific")


## (35) The University of New Hampshire Collection of Insects and Other Arthropods
spec.dist <- symbiota(taxon = "Bombus", db = "UNH server", wait = 4)


## (36) Capturing Californias Flowers
## (37) Consortium of California Herbaria Portal (CCH2)
spec.dist <- symbiota(taxon = "Sisyrinchium", db = "Californias Flowers")


## (38) The Pteridological Collections Consortium
spec.dist <- symbiota(taxon = "Cyathea", db = "Pteridological")


## (39) Macroalgal Consortium Herbarium Portal
spec.dist <- symbiota(taxon = "Amphiplexia", db = "Macroalgal")


## (40) Illinois Natural History Survey’s Biological Collections
spec.dist <- symbiota(taxon = "Lampetra", db = "Illinois")

```


## Currently not supported
```{r not_supported, include = TRUE, eval= FALSE}

## (41) The Lundell Plant Diversity Portal
spec.dist <- symbiota(taxon = "Xanthisma gracile", db = "Lundell") ## not supported, no table

## (42) Minnesota Biodiversity Atlas
spec.dist <- symbiota(taxon = "Picea glauca", db = "Minnesota Biodiversity Atlas") ## not supported, no table

## (43) Oregon Flora # [not public]

```
